Measuring contrast processing in the visual system using SSVEP (and VEP?)

### 2024-03-20 review.qmd
Minor tinkering

*1: a) A typical SSVEP setup: a screen, a grating, a flicker rate: b)
The responses from a single electrode (time domain) c) Frequency
domain.*

@@

import matplotlib.pyplot as plt
import numpy as np
import scipy as scp

@@

```{r}
library(ggplot2)

@@

print(plot)
```

@@

@@

*4: Clinical (Porciatti / Tsai/ Marmite/ Amblyopia / PD?)*
[@porciatti_lack_2000][@tsai_contrast_2011]
*5: Future directions (decoding in frequency domain?, animals? BCI?)*

>>>>

@@

#| label: plotsinewaves
#| fig-cap: "a) A typical SSVEP setup: a screen, a grating, a flicker rate: b) The responses from a single electrode (time domain) c) Frequency domain"
#| fig-cap-location: bottom
#| 
import matplotlib.pyplot as plt
import numpy as np
import scipy as scp

@@

```{r}

library(ggplot2)

@@

print(plot)

@@

#| label: plotspectra
#| fig-cap: "a"
#| fig-cap-location: bottom

@@

*4: Clinical (Porciatti / Tsai/ Marmite/ Amblyopia / PD?)*
[@Porciatti2000; @Tsai2011]
*5: Future directions (decoding in frequency domain?, animals? BCI?)*
